Considering scale in multilayer animal social networks

### 2020-08-26 paper/manuscript.Rmd
specifically which four time periods

<!-- Figure: Fogo ML Net -->
(ref:ml) Multilayer network representing social association of caribou on Fogo Island, Newfoundland between `r timedefs[timecut == 2, format(mindate, '%B %Y')]` and `r timedefs[timecut == 20, format(mindate, '%B %Y')]`. Individual caribou (n = `r DT[, uniqueN(get(idcol))]` females) are represented as nodes in a constant location in layers they were observed. Twelve layers represent combinations of four time windows and three habitat classes (foraging, forest, and open) informed by previous social, spatial and, temporal scale analyses. Intralayer edges represent association between individuals and line thickness is scaled by strength of association (SRI).

>>>>

<!-- Figure: Fogo ML Net -->
(ref:ml) Multilayer network representing social association of caribou on Fogo Island, Newfoundland between `r timedefs[timecut == 2, format(mindate, '%B %Y')]` and `r timedefs[timecut == 20, format(mindate, '%B %Y')]`. Individual caribou (n = `r DT[, uniqueN(get(idcol))]` females) are represented as nodes in a constant position across network layers they were observed in. Twelve layers represent combinations of four time windows (approximately June 2017 - October 2017, November 2017 - May 2018, June 2018 - October 2018, November 2017 - March 2019)  and three habitat classes (foraging, forest, and open) informed by previous social, spatial and, temporal scale analyses. Intralayer edges represent association between individuals and line thickness is scaled by strength of association (SRI).
